\begin{savequote}[75mm] 
Sample Text
\end{savequote}

\chapter{Competition}

\newthought{Traditional tour agencies} differ greatly from our model, but we cannot discount the competition generated from these sources. For example, price is an important factor.

\section{Airbnb}
Airbnb is a website based on the sharing economy that allows people to rent out their lodging to travelers. It currently has over 800,000 property listings in 33,000 cities and 192 countries. Airbnb's business model is the facilitating of transactions between hosts and travelers, without owning any rooms itself, thus allowing it to scale and expand internationally rapidly.

We consider Airbnb a strong competitor as they provide a level of cultural immersion for the guest through themed accommodations, the following and respect of practices and customs of the host, as well as social interaction with the host. Furthermore, they are well poised to expand their offerings to also encourage hosts to also bring their guests out to explore the city.

\section{TravelLocal} 
TravelLocal is another potential competitor. Its motto is "Authentic, Private Trips.Trusted, Locally Owned Travel Companies". The service that they provide is somewhat similar to \name. Firstly, customers will create a customized trip together with their experts, then TravelLocal will connect them with trusted travel agencies and book their trip. They have a fairly large range of destinations offered, from countries such as Kazakhstan and the Caucasus to China. Their focus seems to be more on more exotic areas rather than main tourism hubs.

TravelLocal and similar services may create competition for us due to the fact that normal consumers may feel that their services seem fairly similar to \name. Both \name and TravelLocal emphasises on providing trips that are customizable by the user. TravelLocal also links tourists with tour agencies based in the destination country, so as to provide a more authentic experience. Therefore, product differentiation is required to make \name stand out from competitors such as TravelLocal.

